Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-05-14 minimax.tex
test end-of-line
Normalize all the line endings
tried to add a space to check line-endings
Table 3, 3 runs (4 more ongoing)
clarification on my comment page13

\paragraph{Evaluation of Pessimistic Strategy}
\label{sec:lowRegret}
Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first. Another interesting measure is the average number of questions asked to each participant before reaching zero regret. The results for various sizes are displayed in \cref{tab:questions}. The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the committee to reach a threshold regret $x$, averaged on $20$ runs. We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs. It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).

@@

\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
	\label{tab:twoP500}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
		\midrule
		0 & 0.78 & 0.38 & 0.73 & 0.67 \\
		15 & 0.58 & 0.3 & 0.59	& 0.37  \\
		30 & 0.29 & 0.31 & 0.55 & 0.19 \\
		50 & 0.0 & 0.0 & 0.0 & 0.01 \\
		100 &  &  & 	&   \\
		200 & 	&   &  &  \\
		300 &	& &  & \\
		400 & &  &  &  \\
		500 & &  &  &  \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\Cref{tab:twoP500} shows the MMR value reached in problems of size $m = 10, n = 20$ after $500$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants. These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting. \commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.4$ with $11.05$ question to the chair ($\sigma=12.34$). The data in Table 2 is after 582 questions.}
The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis. However, we observe that asking no questions to the chair does not permit to reach $\MMR\!=\!0$. The strategy, indeed, obtains full knowledge of the profile after an average of 500 questions to the voters but never reaches zero.

>>>>

\paragraph{Evaluation of Pessimistic Strategy}
\label{sec:lowRegret}
Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first. Another interesting measure is the average number of questions asked to each participant before reaching zero regret. The results for various sizes are displayed in \cref{tab:questions}. The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the committee to reach a threshold regret $x$, averaged on $20$ runs. We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs. It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.

%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).

@@

\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
	\label{tab:twoP500}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
		\midrule		
		0	&0.78&	0.38&	0.78&	0.38\\
		15	&0.58&	0.3	&   0.63&   0.26\\
		30	&0.29&  0.31&	0.4&    0.52\\
		50	&0.0&	0.0&	0.0&	0.0\\
		100	&0.21&	0.36&	0.07&	0.12\\
		200	&2.84&	1.52&	1.72&	1.79\\
		300	&6.02&	2.28&	6.79&	0.81\\
		400	&10.95&	0.74&	12.8&	0.92\\
		500	&20.0&	0.0&	20.0&	0.0\\

@@

\Cref{tab:twoP500} shows the MMR value reached in problems of size $m = 10, n = 20$ after $500$ questions, using the Two phases strategy, in the “ca” (chair then agents) and in the “ac” (agents then chair) variants. These numbers are to be compared with the MMR value reached after 500 questions with the Pessimistic strategy (displayed in \cref{fig:linearity}), which is $0.6$; the Pessimistic strategy asks on average $48$ questions to the chair in this setting. \commentBN{This is not true anymore, after 400 questions it reaches $0.9$ with 0 questions to the chair, after 500 questions it reaches $0.47$ ($\sigma = 0.51$) with $11.05$ question to the chair ($\sigma=12.34$). The data in Table 2 is after 582 questions.}\commentBN{Even this comment is not entirely true. We should take the data after 500 questions on the same datasets as the one used in Table3. On the first 3 runs, after 500 questions the regret is $0.62$ ($\sigma = 0.42$) and the number of questions to the committee is $14.33$ ($\sigma = 13.58$). On the first 7 runs, after 500 questions the regret is $0.67$ ($\sigma = 0.45$) and the number of questions to the committee is $13.29$ ($\sigma = 13.11$).}
The line $q_c = 0$, where no question is asked to the chair, suggest that it is possible to obtain a good-quality recommendation while knowing only that the voting rule is a scoring rule with convex weights, which is our basic hypothesis. However, we observe that asking no questions to the chair does not permit to reach $\MMR\!=\!0$. The strategy, indeed, obtains full knowledge of the profile after an average of 500 questions to the voters but never reaches zero.
